---
title: "Why has Pat Aquino never tried Indian Food?"
output: 
  flexdashboard::flex_dashboard:
    #orientation: columns, rows
    vertical_layout: scroll
---

```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(tidytext)
library(stringr)
library(sf)
library(reticulate)
library(treemap)
library(tm)
library(circlize)
library(flexdashboard)
library(plotly)
library(plotrix)
library(tidyverse)
library(tidygraph)
library(ggraph)
library(igraph)
library(echarts4r)
library(ggthemes)
library(widyr)
library(latticeExtra)
#library(scales)
#library(igraph)
#library(ggraph)
#library(widyr)
#library(psych)
#library(cleanNLP)
#library(packcircles)
#library(patchwork)
```

```{r, include=FALSE}
# Importing
df <- read.csv('indian_food.csv')
indstate <- read.csv('indian_states.csv')
indstate <- subset(indstate, select = -X)
ts <- read.csv('indcrops.csv')
```
```{r, include = FALSE}
# Theme
theme_pat <- function () { 
    theme_bw(base_size=12, base_family="Avenir") %+replace% 
        theme(
            panel.background  = element_blank(),
            plot.background = element_rect(fill="gray96", colour=NA), 
            legend.background = element_rect(fill="transparent", colour=NA),
            legend.key = element_rect(fill="transparent", colour=NA)
        )
}

```


```{r, echo = FALSE}
# Have to change some of the variable types (e.g. chr -> factor variables)
# Definitely, diet, flavor_profile, course, state, region
df <- df %>%
  mutate(diet = as.factor(diet),
         flavor_profile = as.factor(flavor_profile),
         course = as.factor(course),
         state = as.factor(state),
         region = as.factor(region))
```

```{r, include=FALSE}
levels(df$diet) # non-vegetarian, vegetarian
levels(df$flavor_profile) # -1, bitter, sour, spicy, sweet
levels(df$course) # dessert, main course, snack, starter
levels(df$state) # -1, etc.
levels(df$region) # -1, central, east, north, ne, south, west
```

```{r, include=FALSE}
# Some variables have -1 as a level. This should be an error and be removed. 
# 255 obs to .... (when NAs are removed)
df2 <- subset(df, flavor_profile != '-1') #226
df2 <- subset(df2, state != '-1') #206
df2 <- subset(df2, region != '-1') #206
df2$region <- droplevels(df2$region)
df2$state <- droplevels(df2$state)
df2$flavor_profile <- droplevels(df2$flavor_profile)
```
```{r, include=FALSE}
shp <- st_read('india_ds.shp')
shp2 <- st_read('india_st.shp')
shp2 <- shp2 %>% rename(
  state = STATE
)
dftest <- df2 %>% mutate(state = toupper(state))
dftest$state <- as.factor(dftest$state)

indstate$state <- as.factor(indstate$State)
dfll2 <- merge(df2, indstate, by = 'state')

lowerstates <- levels(df2$state)
upperstates <- toupper(lowerstates)

test <- merge(dftest, shp2, by = 'state')

a <- dfll2 %>% group_by(state) %>% count(flavor_profile)
b <- a %>% group_by(state) %>% top_n(1, n)
c <- as.data.frame(b)

c  <- c %>% mutate(state = toupper(state))

test2 <- merge(c, shp2, by = 'state') #hopefull this works


#ggplot(test2$geometry) + geom_sf(aes(group = test2$flavor_profile, fill = test2$flavor_profile), show.legend = TRUE) + geom_sf_label(aes(label = test2$state))

# Down to 206
```
```{r, include=FALSE}
# For EDA
eda <- df2[c(3, 6:9)]
#table(eda$flavor_profile, eda$course)
meal <- c('Dessert', 'Main Course', 'Snack', 'Starter')
bitter <- c(0, 3, 1, 0)
sour <- c(0, 1, 0, 0)
spicy <- c(0, 91, 26, 2)
sweet <- c(79, 3, 0, 0)
eda_data <- data.frame(meal, bitter, sour, spicy, sweet)
fig <- plot_ly(eda_data, x =~meal, y = ~bitter, type = 'bar', name = 'Bitter', color = 'black') 
fig <- fig %>% add_trace(y = ~sour, name = 'Sour', color = 'green')
fig <- fig %>% add_trace(y = ~spicy, name = 'Spicy', color = 'red')
fig <- fig %>% add_trace(y = ~sweet, name = 'Sweet', color = 'yellow')
fig <- fig %>% layout(yaxis = list(title = 'Count'), barmode = 'stack')
fig <- fig %>% layout(title = 'Distribution of Flavors across Meal Types')
fig <- fig %>% layout(theme = theme_pat())
```
```{r, include=FALSE}
# For Text
text_data <- df2[c(2, 6)]
mod_text<- text_data %>% 
  mutate(flavor_profile = tolower(flavor_profile),
         flavor_profile = str_trim(str_replace_all(flavor_profile, "\\[.*?\\]", "")))
text_tokens <- mod_text %>%
  select(line = flavor_profile, ingredients) %>% 
  unnest_tokens(word, ingredients, strip_numeric = TRUE) %>%
  mutate(word = str_replace_all(word, "'s$", ""))
tidy_tokens_text <- text_tokens %>% 
  anti_join(stop_words, by = "word")

custom_stop_words <- bind_rows(data_frame(word = c('food'), 
                                          lexicon = c("custom")), 
                               stop_words)

tidy_tokens_text <- tidy_tokens_text %>% 
  anti_join(custom_stop_words, by = "word")

word_ratios_sweet_spicy <- tidy_tokens_text %>%
  filter(line %in% c("sweet", 'spicy')) %>% 
  count(word, line) %>%
  filter(n >= 10) %>%
  spread(line, n, fill = 0) %>%
  mutate(across(where(is.numeric), ~(.+1)/sum(.+1))) %>% # Avoiding 0/0 issues
  # mutate_if(is.numeric, funs((. + 1) / sum(. + 1))) %>% 
  mutate(log_ratio = log2(sweet / spicy)) %>% # log base 2 scale
  arrange(desc(log_ratio))

knitr::kable(word_ratios_sweet_spicy %>% 
               arrange(abs(log_ratio)) %>% 
               head(10), "html") %>% 
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))


```
```{r}
# For Networks
region_text <- df2[c(2, 9)]
region_text<- region_text %>% 
  mutate(region = tolower(region),
         region = str_trim(str_replace_all(region, "\\[. *?\\]", "")))
region_tokens <- region_text %>%
  select(line = region, ingredients) %>% 
  unnest_tokens(word, ingredients, strip_numeric = TRUE) %>%
  mutate(word = str_replace_all(word, "'s$", ""))
region_tokens_text <- region_tokens %>% 
  anti_join(stop_words, by = "word")
#table(region_tokens_text$line, region_tokens_text$word)
```
```{r}
vals <- c(2, 0, 3, 0, 1,
          9, 16, 2, 3, 2,
          15, 4, 2, 2, 30,
          6, 3, 0, 9, 2,
          12, 8, 22, 14, 1,
          48, 15, 12, 12, 4)
col.pal <- c(flour = 'red', sugar = 'yellow', dal = 'black', rice = 'blue', masala = 'orange')
region_matrix <- matrix(vals, nrow = 5, dimnames = list(c('flour', 'sugar', 'dal', 'rice', 'masala'), c('Central', 'East', 'North', 'NorthEast', 'South', 'West')))
```
```{r}
# For Time Series
e <- ts %>% mutate(highlight = ifelse(Crop == 'Sugarcane', 'Sugar', 'Other')) %>%
  ggplot(aes(x = Year, y = N, group = Crop, color = highlight, size = highlight)) + 
  geom_line() + 
  scale_color_manual(values = c("#69b3a2", "lightgrey")) +
  scale_size_manual(values=c(.2,1.5)) +
  theme(legend.position="right") +
  ggtitle('Annual Wholesale Price Index of Agriculture Produce in India') + theme_pat()
```

Column {data-width=400}
-----------------------------------------------------------------------

#### Introduction

Though I really love food; I am very picky. There are certain things I will not eat namely spicy food. I have a really low tolerance on spicy food--and yet I do not understand how some people enjoy eating them. Growing up, one of my childhood friend is Indian. After school, I got invited to my friend's house to play board games and chess. My friend's parents are very hospitable and always offered me food; sadly I always had to refuse or reject their offer. Reminiscing from the past, I would like to try one, but how do I choose which Indian dish to make?

#### Starting from Selecting an Indian State/Region:
### Geographical

```{r}
ggplot(test2$geometry) + geom_sf(aes(group = test2$flavor_profile, fill = test2$flavor_profile), show.legend = TRUE) + ggrepel::geom_label_repel(aes(label = test2$state, geometry = geometry), stat = 'sf_coordinates', min.segment.length = 0) + theme_light() + ggtitle('Dominant Recipe Flavor for Each Indian State') + ylab('Latitude') + xlab('Longitude') + guides(fill = guide_legend(title = 'Flavor'))

#ggplotly(geo, tooltip = test2$state)

```

Column {data-width=300}
-----------------------------------------------------------------------

#### Why are there so many Indian States with Sweet Label?
It seems odd that there are Indian states that have dominantly sweet recipes. Therefore, I tried to look into the meal course distribution if it could explain something.

#### Heavy Contrast between Sweet and Spicy
It is now apparent that the bulk of the data is filled with sweet and spicy Indian recipes. It does make sense now that why some states are dominated by sweet recipes; they just have a lot of dessert recipes that overshadows the main courses. 

### Exploratory
```{r}
fig
```

-----------------------------------------------------------------------



### Text

```{r}
word_ratios_sweet_spicy %>%
  group_by(direction = ifelse(log_ratio < 0, 'spicy', 'sweet')) %>%
  top_n(15, abs(log_ratio)) %>%
  ungroup() %>%
  mutate(word = reorder(word, log_ratio)) %>% # Re-ordering factor for plotting
  ggplot(aes(word, log_ratio, color = direction)) +
  geom_segment(aes(x = word, xend = word,
                   y = 0, yend = log_ratio),
               size = 1.1, alpha = 0.6) +
  geom_point(size = 2.5) +
  coord_flip() +
  theme_pat() +
  labs(x = NULL, 
       y = "Relative Occurrence",
       title = "Distinguishable Ingredients between Spicy and Sweet Indian Foods") +
  theme(plot.title = element_text(hjust = 0.5),
        legend.title = element_blank()) +
  scale_y_continuous(breaks = seq(-6, 6), 
                     labels = c("64x", "32x", "16x","8x", "4x", "2x", # This is due to log base 2
                                "Same", "2x", "4x", "8x", "16x", "32x", "64x")) +
  scale_color_manual(values = c("#daad62", "#9c311f")) 
```

Column {data-width=400}
-----------------------------------------------------------------------

#### Flour is Dominated in the West, while Sugar is evenly dispersed

### Network
```{r}
chordDiagram(region_matrix, grid.col =  col.pal, title(main = 'Top Ingredients Distribution by Region')) 
```

### Time Series
```{r}
ggplotly(e)
```