---
title: "task2"
author: "Patrick Aquino"
date: "10/21/2020"
output: html_document
---

# Task

What is the distribution of all loans and what are their characteristics?

# Procedure
### 1. Import dataset (accounts_analytical and transactions)
### 2. Convert Loan_Default as factor
### 3. Create distributions for each type of loans
### 4. Create subset of all TRUE for Default_loans
### 5. Make loan_term factor
### 6. Visualize


# Import

```{r import, include=FALSE}
acc <- read.csv('accounts_analytical.csv')
trans <- read.csv('transactions.csv')
```

# Convert Loan Default as Factor
```{r loand, include=T}
acc$loan_default <- as.factor(acc$loan_default)
```

# Distributions of Loans

```{r vis, include= T}
library(ggplot2)
vis <- ggplot(data = acc, mapping = aes(x = loan_amount, y = loan_payment, color = loan_default, alpha = 0.15)) + geom_point() + facet_wrap(. ~ loan_term, ncol =3)

vis + labs(title = 'Distributions of Loans per Loan Term', y = 'Loan Payment', x = 'Loan Amount')
```

# Create subset
```{r chars, include=T}
defs <- subset(acc, loan_default == 'TRUE')
defs$paid <- defs$loan_payment / defs$loan_amount
```

# Make loan_term factor
```{r termf, include=T}
defs$loan_term <- as.factor(defs$loan_term)
```

# Visualization
```{r viss, include=T}
vis <- ggplot(data = defs, mapping = aes(x = loan_amount, y = loan_payment, size = paid, shape = loan_term, alpha = 0.15)) + geom_point() 


vis + labs(title = 'Distribution of Defaulted Loans with other Characteristics', y = 'Loan Payment', x = 'Loan Amount')
```
