---
title: "task4"
author: "Patrick Aquino"
date: "10/21/2020"
output: html_document
---

# Task: 

For the account with the highest number of transactions, make a time series line plot for the behavior of the account over time, including all the debits and credits, the different methods, and with the different categories.

# Procedure:
### 1. Import dataset (accounts_analytical and transactions)
### 2. Convert $acc_creation_date and $loan_date into date variables
### 3. Find the account with the highest transactions 
### 4. Subset the account by type
### 5. Rename NA levels into Not Specified
### 6. Plot time series

# Import

```{r import, include=TRUE}
acc <- read.csv('accounts_analytical.csv')
trans <- read.csv('transactions.csv')
```

# Coverting Data Variables
```{r datevar, include=TRUE}
library(lubridate)
acc$acct_creation_date <- ymd(acc$acct_creation_date)
acc$loan_date <- ymd(acc$loan_date)
trans$date <- ymd(trans$date)
```

# Find the Account with most transactions
```{r mosttrans, include=TRUE}
findacc <- table(trans$account_id)
names(findacc[which.max(findacc)]) # '8261'
```

# Subset Data
```{r subset, include=T}
subset <- trans[trans$account_id == '8261',]
```

# Subset Part 2 by Type
```{r subset2, include=T}
credit <- subset[subset$type == 'credit',]
debit <- subset[subset$type == 'debit',]
```

# Renaming Levels
```{r renam, include=T}
levels(credit$method)[1] <- 'not specified'
levels(debit$method)[1] <- 'not specified'
levels(credit$category)[1] <- 'not specified'
levels(debit$category)[1] <- 'not specified'
```

# Plot Time Series for Account_ID #8261
```{r plot, include=T}
library(ggplot2)
vis <- ggplot(credit, aes(x=date, y=balance, )) + geom_line(color = "steelblue") + geom_point()
vis + facet_wrap(. ~ category, ncol = 2) + labs(title = 'Account #8261 Credit Transaction History by Categories')
vis + facet_wrap(. ~ method, ncol = 2) + labs(title = 'Account #8261 Credit Transaction History by Method')

vis <- ggplot(debit, aes(x=date, y=balance, )) + geom_line(color = "steelblue") + geom_point()
vis + facet_wrap(. ~ category, ncol = 2) + labs(title = 'Account #8261 Debit Transaction History by Categories')
vis + facet_wrap(. ~ method, ncol = 2) + labs(title = 'Account #8261 Debit Transaction History by Method')
```
