---
title: "task1"
author: "Patrick Aquino"
date: "10/21/2020"
output: html_document
---

# Task:

Explore all accounts. Create visualizations that combine (or these account characteristics): \
- Whether an account has a credit card or not \
- Whether an account has a loan or not \
- The average balance for the account



# Procedure
### 1. Import dataset (accounts_analytical and transactions)
### 2. Convert $credit_cards to binary 
### 3. Convert $loan_status to binary
### 4. Find average $balance per account
### 5. Create a new dataframe
### 6. Merge account, credit_Card, loan_status and avg_balance
### 7. Create new variable with 4 levels combining credit card (yes or no) and loan (yes or no)
### 8. Splitting the BIG dataframe into smaller dataframes to make a more comprehensible visuals
### 9. Create box plot of the average balances and color with the 4 levels


# Import

```{r import, include=TRUE}
acc <- read.csv('accounts_analytical.csv')
trans <- read.csv('transactions.csv')
```

# Convert to Binarys 
```{r binary, include=TRUE}
acc[is.na(acc)] = 0 # converting NAs to 0
acc$cc_binary <- ifelse(acc$credit_cards == 0, 0, 1)
acc$loans_binary <- ifelse(acc$loan_status == 'current' | acc$loan_status == 'expired', 1, 0)
```

# Find average balance per account
```{r average, include=TRUE}
avg <- with(trans, tapply(balance, account_id, mean))
c <- as.data.frame(avg)
c$avg <- as.numeric(c$avg)
uni <- unique(trans$account_id)
c$account_id <- uni
```

# Merge Balance per Account
```{r newdf, include=TRUE}
library(dplyr)
final <- merge(acc, c, by = 'account_id')
final <- final %>%
  select(account_id, cc_binary, loans_binary, avg)
```

# Create a new variable combining Credit Card and Loans
```{r final, include= TRUE}
final <- final %>%
  mutate(cc_loans =  case_when(cc_binary == '1' & loans_binary == '1' ~ 'both credit card and loans',
                               cc_binary == '1' & loans_binary == '0' ~ 'just credit card',
                               cc_binary == '0' & loans_binary == '1' ~ 'just loans',
                               cc_binary == '0' & loans_binary == '0' ~ 'neither credit card nor loans'))
final$cc_loans <- as.factor(final$cc_loans)
```

# splitting the big dataframe into smaller dataframes
```{r}
# 4500/4 = 1125
first <- final[1:1125, ]
second <- final[1126:2300, ]
third <- final[2301:3425, ]
fourth <- final[3450:4500, ]

```

# Do Visualizations for R
```{r visr, include= TRUE}
library(ggplot2)

fvis <- ggplot(first, aes(x= account_id, y= avg, fill = cc_loans)) +  geom_bar(stat = 'identity') 
svis <- ggplot(second, aes(x= account_id, y= avg, fill = cc_loans)) +  geom_bar(stat = 'identity') 
tvis <- ggplot(third, aes(x= account_id, y= avg, fill = cc_loans)) +  geom_bar(stat = 'identity') 
fovis <- ggplot(fourth, aes(x= account_id, y= avg, fill = cc_loans)) +  geom_bar(stat = 'identity') 
```

# First Quartile Accounts
```{r first, include=TRUE}
fvis + labs(title = "Average Balance for first Quartile Account IDs", x = "Account ID", y = "Balance") 
```

# Second Quartile Accounts
```{r second, include=TRUE}
svis + labs(title = "Average Balance for second Quartile Account IDs", x = "Account ID", y = "Balance") 
```

# Third Quartile Accounts
```{r third, include=TRUE}
tvis + labs(title = "Average Balance for third Quartile Account IDs", x = "Account ID", y = "Balance") 
```

# Fourth Quartile Accounts
```{r fourth, include=TRUE}
fovis + labs(title = "Average Balance for fourth Quartile Account IDs", x = "Account ID", y = "Balance") 

```



